---
title: "NEW"
author: "Darlington"
date: "2020/8/28"
output: html_document
---
```{r}
library(pROC)
library("knitr")
library("kableExtra")
library(readxl)

dat=read_excel("NEW.xlsx",sheet = "2")
dat1=read_excel("NEW.xlsx",sheet = "VM")
dat2=read_excel("NEW.xlsx",sheet = "MB")
#par(las=2, font=5, bty='l', ps=6)
#boxplot(dat[,4:13], cex=0.5, pch=16, col=runif(nrow(dat), 1, nrow(dat)))
```


## VB
```{r}

library(Hmisc)

dat$CRP=impute(dat$CRP,median)
dat$PCT=impute(dat$PCT,median)
dat$NC=impute(dat$NC,median)
dat$MC=impute(dat$MC,median)
dat$EC=impute(dat$EC,median)
dat$WBC=impute(dat$WBC,median)
dat$LC=impute(dat$LC,median)

dat$LMR=dat$LC/dat$MC
dat$NLR=dat$NC/dat$LC
```
library(purrr)
logit_reg<-function(x){
  coef(summary(glm(t~x, data=dat,family="binomial")))[2,]
}
result<-map(dat[,2:18],logit_reg)
result

## multivariate logistic regression
```{r}
library(AUC)

## whole
pre<-glm(T~AGE + SEX + LMR + NLR + COUGH + FEVER +Rhinorrhea +CRP, data = dat,family = binomial("logit"))
glm.step<-step(pre) 
summary(glm.step)


glm.probs <- predict.glm(pre, type="response", newdata=dat)
sum(ifelse(glm.probs>0.5,1,0)==dat$T)
drop1(glm.step)


plot(roc(glm.probs,as.factor(dat$T)), col=rainbow(10), main = "WHOLE")
Ir.auc<- auc(roc(glm.probs, as.factor(dat$T)))
text(0.8,0.2,labels=paste('AUC', round(Ir.auc,3),sep = ''),cex = 1.2)


```




## MB
#```{r}


library(Hmisc)
dat2$CRP=impute(dat2$CRP,median)
dat2$PCT=impute(dat2$PCT,median)
dat2$NC=impute(dat2$NC,median)
dat2$MC=impute(dat2$MC,median)
dat2$EC=impute(dat2$EC,median)
dat2$WBC=impute(dat2$WBC,median)
dat2$LC=impute(dat2$LC,median)

dat2$CPR=dat2$CRP/dat2$PCT
dat2$LMR=dat2$LC/dat2$MC
dat2$NLR=dat2$NC/dat2$LC
```

library(purrr)
logit_reg<-function(x){
  coef(summary(glm(t~x, data=dat2,family="binomial")))[2,]
}
result<-map(dat2[,2:18],logit_reg)
result



## multivariate logistic regression
#```{r}
library(AUC)

## whole
pre<-glm(t~NC, data = dat2,family = binomial("logit"))
glm.step<-step(pre) 
summary(glm.step)

glm.probs <- predict.glm(pre, type="response", newdata=dat2)
sum(ifelse(glm.probs>0.5,1,0)==dat2$t)
drop1(glm.step)


plot(roc(glm.probs,as.factor(dat2$t)), col=rainbow(10), main = "WHOLE")
Ir.auc<- auc(roc(glm.probs, as.factor(dat2$t)))
text(0.8,0.2,labels=paste('AUC', round(Ir.auc,3),sep = ''),cex = 1.2)



```



## model
#```{r}
set.seed(1234)

N=length(dat2$t)

ind=sample(2,N,replace=TRUE,prob=c(0.7,0.3))

 

dat_train=dat2[ind==1,]
dat_test=dat2[ind==2,]

pre=glm(t~AGE+CPR+OUTU+FEVER+NLR+COUGH+Rhinorrhea,data=dat_train,family=gaussian(link="identity"))

summary(pre)

 

real=dat_test$t
predict_=predict.glm(pre,type="response",newdata=dat_test)
predict=ifelse(predict_>0.5,1,0)
dat_test$predict=predict

head(dat_test)

true_value=dat_test$t
predict_value=dat_test[,22]

error=predict_value-true_value
accuracy=(nrow(dat_test)-sum(abs(error)))/nrow(dat_test)
precision=sum(true_value & predict_value)/sum(predict_value)
recall=sum(predict_value & true_value)/sum(true_value)
F_measure=2*precision*recall/(precision+recall) 

print(accuracy) 
print(precision) 
print(recall) 
print(F_measure) 



library(ROCR)      
pred <- prediction(predict_,true_value)
performance(pred,'auc')@y.values
perf <- performance(pred,'tpr','fpr') 

plot(perf) 

```
## VM
#```{r}

library(Hmisc)

dat1$CRP=impute(dat1$CRP,median)
dat1$PCT=impute(dat1$PCT,median)
dat1$NC=impute(dat1$NC,median)
dat1$MC=impute(dat1$MC,median)
dat1$EC=impute(dat1$EC,median)
dat1$WBC=impute(dat1$WBC,median)
dat1$LC=impute(dat1$LC,median)

dat1$CPR=dat1$CRP/dat1$PCT
dat1$LMR=dat1$LC/dat1$MC
dat1$NLR=dat1$NC/dat1$LC



```


## multivariate logistic regression
#```{r}
library(AUC)

## whole
pre<-glm(t~CRP, data = dat2,family = binomial("logit"))
glm.step<-step(pre) 
summary(glm.step)

glm.probs <- predict.glm(pre, type="response", newdata=dat2)
sum(ifelse(glm.probs>0.5,1,0)==dat2$t)
drop1(glm.step)


plot(roc(glm.probs,as.factor(dat2$t)), col=rainbow(10), main = "WHOLE")
Ir.auc<- auc(roc(glm.probs, as.factor(dat2$t)))
text(0.8,0.2,labels=paste('AUC', round(Ir.auc,3),sep = ''),cex = 1.2)



```

library(purrr)
logit_reg<-function(x){
  coef(summary(glm(t~x, data=dat1,family="binomial")))[2,]
}
result<-map(dat1[,2:18],logit_reg)
result




## model
#```{r}
set.seed(1234)

N=length(dat1$t)

ind=sample(2,N,replace=TRUE,prob=c(0.7,0.3))

 

dat_train=dat1[ind==1,]
dat_test=dat1[ind==2,]

pre=glm(t~NC,data=dat_train,family=gaussian(link="identity"))

summary(pre)

 

real=dat_test$t
predict_=predict.glm(pre,type="response",newdata=dat_test)
predict=ifelse(predict_>0.5,1,0)
dat_test$predict=predict

head(dat_test)

true_value=dat_test$t
predict_value=dat_test[,22]

error=predict_value-true_value
accuracy=(nrow(dat_test)-sum(abs(error)))/nrow(dat_test)
precision=sum(true_value & predict_value)/sum(predict_value)
recall=sum(predict_value & true_value)/sum(true_value)
F_measure=2*precision*recall/(precision+recall) 

print(accuracy) 
print(precision) 
print(recall) 
print(F_measure) 



library(ROCR)      
pred <- prediction(predict_,true_value)
performance(pred,'auc')@y.values
perf <- performance(pred,'tpr','fpr') 

plot(perf) 

```
